Tree size, (microhabitat)?, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2019-09-08 manuscript/climate_sensitivity_draft.Rmd
Update climate_sensitivity_draft.Rmd
a few minor updates

Commonly measured traits including wood density (REFS), leaf mass per area [@abrams_adaptations_1990] [@guerfel_impacts_2009], and ring porosity (Elliot et al. 2015, Friedrichs et al. 2009) have been linked to drought responses and likely correlated with drought resistance in this forest. However, we hypothesize that leaf hydraulic traits such as leaf area shrinkage upon dessication (PLA) and turgor loss point (TLP), which are emerging as potentially more informative traits but whose effect on drought resistance has never been tested (CONFIRM), will prove better predictors.

@@

We need to understand the the factors confirming drought vulnerability or resistance not only for extreme droughts with dramatic impacts on tree growth and mortality, which tend to dominate the literature [@bennett_larger_2015] (REFS), but also for more modest but frequent droughts--e.g., those with historical return intervals on the order of a decade.

>>>>

Commonly measured traits including wood density (REFS), leaf mass per area [@abrams_adaptations_1990] [@guerfel_impacts_2009], and ring porosity (Elliot et al. 2015, Friedrichs et al. 2009) have been linked to drought responses and likely correlated with drought resistance in this forest. However, we hypothesize that leaf hydraulic traits such as leaf area shrinkage upon dessication (PLA; REF) and turgor loss point (TLP; REF), which are emerging as potentially more informative traits but whose effect on drought resistance has never been tested, will prove better predictors.

@@

We need to understand the the factors confirming drought vulnerability or resistance not only for extreme droughts with dramatic impacts on tree growth and mortality, which tend to dominate the literature [@bennett_larger_2015] (*Stovall_new*; REFS), but also for more modest but frequent droughts--e.g., those with historical return intervals on the order of a decade.
